---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mminer

<!-- badges: start -->
<!-- badges: end -->

The mminer package is a simple wrapper for [Marketing Miner Profilers API](https://help.marketingminer.com/en/article/profilers-api/). Currently it provides functions to fetch search volume data only. Fetched data are cached locally in a file and used to save credits when necessary.

## Installation

You can install the development version of mminer from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MarekProkop/mminer")
```

## After instalation (important)

You have to get your own [API key for Marketing Miner Profilers API](https://www.marketingminer.com/en/settings/api-settings) first. Then save the key in an environment variable named 'MARKETING_MINER_API_KEY'. If you don't do that, you will have to provide your API key in the `api_key` argument of all function calls.

## Examples

To get search volume data for a single search query:

```{r example}
library(mminer)
get_volume_data("seo", lang = "cs")
```

To get search volume data for multiple search queries:

```{r}
queries <- c("seo", "seo optimalizace", "seo company")
get_volume_data(queries, lang = "cs")
```

To retrieve data from cache:

```{r}
get_volume_cache()
```

To calculate costs:

```{r}
queries <- c("seo", "seo optimalizace", "seo company", "seo specialista")
get_volume_cost(queries)
```

To delete the cache file:

```{r}
delete_volume_cache()
```

## About caching

By default the cache is a file (rds) in the _mminer-cache_ folder, which is automaticaly created in the current working folder. The folder itself is not removed by the `delete_volume_cache()` function.

You can change the cache folder by the `cache_path` argument, e.g.:

```{r}
get_volume_data("seo", lang = "cs", cache_path = tempdir())
```

Now the default cache dosen't exist:

```{r}
get_volume_cost("seo")
```

But in `temdir()` it does:

```{r}
get_volume_cost("seo", cache_path = tempdir())
```

```{r}
delete_volume_cache(tempdir())
```

